---
title: "And The Survey Says..."
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(jsonlite)
library(knitr)
setwd("/Users/Joycie/info498f/assignment-7-group-coding")
source("scripts/summary.R")
source("scripts/secondChart.R")

data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")
```

### This is a report on the survey students in INFO 498F Winter 2016 took before starting the course.
Here are some facts we have found: <br>
 1. There are `r info_function(data) [['Seahawks_fan']]` Seahawks fans <br>
 2. There are also `r info_function(data) [['info_intended']]`  intended Informatics majors <br>
 3. The person who has visited the most countries has visited `r info_function(data)  [['most_countries']]` countries
 <br>
 <br>
 
### Here is a summary table of the class standings across the class

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# makes summary table
kable(info_function(data)[['class_standing']])
```

### This chart shows

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# makes first plot 
```

### This is second plot will compare the number of people who understand Terminal.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# makes second plot of the number of people who understood Terminal 
make_plot(data)
```

